\addcontentsline{toc}{chapter}{Acknowledgments}
\chapter*{Acknowledgments}
I wish to acknowledge, first and foremost, the patience, guidance and support of my supervisors Martha Savage and John Townend, who allowed me to careen from project to project, eventually happening upon the document you're holding, and learning an immeasurable amount in the process. Thank you also to Steve Sherburn, Sandra Bourguignon, Zara Rawlinson and rest of team at GNS Science for installing and maintaining the seismic network used here, for providing advice and scientific context and for creating the earthquake catalog from which all of this began.

A very large thank you indeed to Mercury NZ Ltd. (the artist formerly known as Mighty River Power), the Tauhara no. 2 Trust and the Rotokawa Joint Venture for fully finding all aspects of this project and for generously providing access to the large and varied dataset from which I learned so much. A similarly large thank you goes out to the fantastic, helpful staff at the New Zealand eScience Infrastructure for providing many (misused) hours of computing time on the PAN cluster and for their patience when things often went awry.

To the staff on floor 5 of the Cotton building including: Rupert, Huw, Tim and Adrian, thank you for providing banter, lunchtime monologues, pertinent skiing advice and unparalleled swagger. To the glue holding this circus together, Aleksandr Beliaev, many thanks for being exceptionally helpful and always willing to share an encyclopedic knowledge of the world of computing.

I would be remiss in forgetting to acknowledge each of the cohort of graduate students to have passed through these halls including: Jesse, Rachel, Franny, LMB, Gabe, Stefan, Hamish, C\'{e}cile, Abhi, Pasan, Hubert, Katrina, Weiwei, Nico, Dan, Konrad, Lucie and all of the others I may have missed. Thank you for making this place a lively space full of character and fun. To my New Zealand family Dani, Andy, Kostas, Dom, B-Chow, Lauren, Jamey, KJ, Calum, Emily, Geoff, Elisa, C\'{e}line and the Hoogs, thank you for making this place home.

Thank you to Stefan for his diligent work in conducting the automated S-picking used throughout this work and for having an appreciation for \textit{real} hockey.

I want to specifically thank Mr. Calum J. Chamberlain for serving as a de-facto supervisor over the last three-and-a-bit years. Thank you for providing me with a sterling example of what effort, caring and lovely code looks like.

Without the vision of Steve Sewell, in particular, this project would never have existed. To Steve, I offer the most sincere thank you for opening up his deep knowledge of all things Ngatamariki, Rotokawa, and geothermal from which I could always draw when I was confused. This project wouldn't be half as good without your contribution. Beers on me for life.

To Ashley, `thank you' is woefully inadequate. For patiently stumbling into a three-year experiment of much greater proportions and difficulty than this PhD, you have my unending appreciation and gratitude.

Finally, to Mom and Dad, your contribution to this accomplishment is immeasurable. Thank you for absolutely everything. This is for you.